Models

### 2021-10-06 analysis/05_model_metrics.Rmd
covariates as fixed effects

Create dataframe of models to fit
```{r}
raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "FRic", "FEve", "FDiv", "Jaccard_base"), 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

log_value_mods <- tibble(metric_name = c("S"), 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
                         realm = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
                         climate = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

>>>>

Create dataframe of models to fit
```{r}
# raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "FRic", "FEve", "FDiv", "Jaccard_base"), 
#                          base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
#                          taxa = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
#                          realm = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
#                          climate = "value ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
#   pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")
# 
# log_value_mods <- tibble(metric_name = c("S"), 
#                          base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
#                          taxa = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|taxa)",
#                          realm = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|realm)",
#                          climate = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID) + (year_scaled|climate)") %>%
#   pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

raw_value_mods <- tibble(metric_name = c("SES_FRic", "SES_FEve", "SES_FDiv", "FRic", "FEve", "FDiv", "Jaccard_base"), 
                         base = "value ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "value ~ year_scaled + as.factor(taxa) + (year_scaled|study_id/rarefyID)",
                         realm = "value ~ year_scaled + as.factor(realm) + (year_scaled|study_id/rarefyID)",
                         climate = "value ~ year_scaled + as.factor(climate) + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")

log_value_mods <- tibble(metric_name = c("S"), 
                         base = "logvalue ~ year_scaled + (year_scaled|study_id/rarefyID)",
                         taxa = "logvalue ~ year_scaled + as.factor(taxa) + (year_scaled|study_id/rarefyID)",
                         realm = "logvalue ~ year_scaled + as.factor(realm) + (year_scaled|study_id/rarefyID)",
                         climate = "logvalue ~ year_scaled + as.factor(climate) + (year_scaled|study_id/rarefyID)") %>%
  pivot_longer(cols = c(base, taxa, realm, climate), names_to = "model_id", values_to = "formula")
